### 2017-03-13 paper/oopsla17-submission/evaluation.tex
another dimension of shrinking

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  % ybar stacked,
  width=12cm,
  height=8cm,
  title={Impact of Feature Set on Accuracy},
  ylabel={Accuracy},
  %ymin=0.2,
  ymax=1,
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={op+type+size, op+context+type+size, op+context-has+type+size, op+context-count+type+size},
  % enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={Type, Context, Context-Has, Context-Count},
  x tick label style={rotate=45},
  reverse legend,
  transpose legend,
  legend style={legend pos = outer north east, legend columns=4},
]
% \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% \addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\HiddenBench};
% \addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\HiddenBench};

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  % ybar stacked,
  width=12cm,
  height=8cm,
  title={Impact of Feature Set on Accuracy},
  ylabel={Accuracy},
  %ymin=0.2,
  ymax=1,
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={op+type+size, op+context+type+size, op+context-has+type+size, op+context-count+type+size},
  % enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={Type, Context-Is, Context-Has, Context-Count},
  x tick label style={rotate=45},
  reverse legend,
  transpose legend,
  legend style={legend pos = outer north east, legend columns=4},
]
% \addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\HiddenBench};
% \addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\HiddenBench};
% \addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\HiddenBench};
